
\subsection{Login and Register}
As a manager, I want to register an account, so I can go through all the functions every time I login. Besides,if I forget my password, there should be a password find back method, so I can find back my account.

\subsection{Functions List}
As a manager, I want all the functions to be showed in one page, so that I can easily start my work by clicking certain functions.

\subsection{Students Register}
As a manager, I should have the right to add students to our system, so later I can build a class by selecting students who have enrolled in that class. For each student,some basic student information can be provided to the system, such as last name, first name and student ID number.

\subsection{Teachers Register}
As a manager, I should have the right to add professors to our system, so later I can allocate professors to different classes. For each professor, some basic professor information can be provided to the system, such as last name, first name and professor ID number.

\subsection{Build Classes}
As a manager, I should have the right to create a new class, so that I can add students to the class.As I add students to a new class, there should be a searching method based on name or ID number, so that I can easily find certain students instead of going over all students.Besides, when a student drops a class, I can remove him/her from that class.

\subsection{Create Surveys}
As a manager, I want to create surveys for different classes, so that students can make comments about their classes. The content of surveys should also be able to revise so more specific questions could be added. When students update their comments, I should be able to check their surveys, so I can talk to professors to make classes better.