\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{indentfirst}

\begin{document}

\title{User Story of Manager}
\author{Huasheng Li}
\date{January 14, 2019}
\maketitle
\section*{Objective}
As a manager, I want to have an account to log in the manager interface, So that I can manage all classes,students and professors information.

\section*{Acceptance Criteria}
\begin{itemize}
\item[$\bullet$] Allow manager to register a new account.
\item[$\bullet$] Methods to find back password when user forget it.
\item[$\bullet$] show all functions for manager, such as students class management, students management etc.
\item[$\bullet$] Allow user to add information of students to system. Include first name, last name and student ID number.
\item[$\bullet$] Allow user to add information of professors to system. Include first name, last name and professor ID number.
\item[$\bullet$] Allow user to build new classes by selecting students and professors enrolled.
\item[$\bullet$] Allow user create survey about professors and classes.
\end{itemize}

\section*{Definition of Done}
\begin{itemize}
\item[$\bullet$] After the request from the front-end, the back-end can give the correct response without mistake.
\item[$\bullet$] Passes the tests according to each acceptance criteria
\item[$\bullet$] Passes the tests from the combination of each criteria
\item[$\bullet$] The layout approved by the UI team
\item[$\bullet$] Make tests on various users' mobiles to test its stability.
\end{itemize}

\end{document}